---
title: "SRM"
author: "Qian"
date: "2025-03-18"
output: html_document
---

# Load the tidyverse package below
```{r T101, warning=FALSE, message=FALSE}
# Load the tidyverse package below
cat("\f")
rm(list=ls())

# Init
graphics.off()

#install.packages("ez")
#("phia")
#install.packages("effsize")
#install.packages("srm")
#install.packages("TripleR")
library("MASS")
library(ez)
library(afex)
library(phia)
library(doBy)
library(effsize)
library(lmerTest);
library(dplyr);
library(srm);
library(ggplot2)
library(TripleR)

setwd(dirname(rstudioapi::getActiveDocumentContext()$path))


#Import data
file_name = "data/behavior/all_data_df.csv"

#read data
data = read.table(file_name, header=TRUE,sep=',')
head(data)

#defining outcomes
measure			          <-as.numeric(data$measure)

#defining predictors (categorical)
participant_condition 	<- as.factor(data$participant_condition)
participant_condition   <- relevel(participant_condition, "S")
other_condition 		    <- as.factor(data$other_condition)
other_condition         <- relevel(other_condition, "S")
participant_nb			    <- as.factor(data$user_id)
interacting_partner			<- as.factor(data$other_id)
question_content		    <- as.factor(data$question_content)
group_id		            <- as.factor(data$sid)

#create new dataframe
all_data=data.frame( measure, participant_condition , interacting_partner, other_condition, participant_nb, question_content, group_id )

## -------------------------------------- ##
## -------------------------------------- ##
## GLMM Analysis ------------------------ ##
## -------------------------------------- ##
## -------------------------------------- ##

# Choose the question you want to anlayse
#question = "conversation_quality"
#question = "liked"
question = "other_liked"
#question = "video_conf_quality"

clean_data <- all_data[all_data$question_content == question,]
head(clean_data)


#Social relation Model
RR.style("perception")

#Round Robin
RR1 <- RR(measure ~ participant_nb * interacting_partner | group_id, data = clean_data, na.rm = TRUE)
RR1


#Missing values
plot_missings(measure ~ participant_nb * interacting_partner | group_id, data = clean_data, show.ids = FALSE)

#Variance covariance
plot(RR1)


RR1$effects #measure perceiver and target
RR1$effectsRel

result_file = paste("data/behavior/srm/",question,".csv", sep="")
write.csv(RR1$effectsRel, result_file) #Relationships

df = data(likingLong)


str(likingLong)
```

```

```{r T101, warning=FALSE, message=FALSE}

# Load required libraries
library(lme4)
library(ggplot2)

# Function to run GLMM for each SRM dataset
run_srm_glmm <- function(data, title) {
  # Ensure factors are properly set
  data$participant_condition <- as.factor(data$participant_condition)
  data$other_condition <- as.factor(data$other_condition)

  # Run the GLMM
  glmm_model <- lmer(relationship ~ participant_condition * other_condition + 
                      (1 | participant_nb) + (1 | interacting_partner), 
                      data = data)
  
  # Print summary
  print(summary(glmm_model))
  
  # Plot results
  ggplot(data, aes(x = participant_condition, y = relationship, color = other_condition)) +
    geom_point(alpha = 0.3, position = position_jitter(width = 0.2)) +
    stat_summary(fun = mean, geom = "point", size = 4, position = position_dodge(0.2)) +
    stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, position = position_dodge(0.2)) +
    labs(title = title, x = "Participant Condition", y = "Relationship Rating (SRM)") +
    scale_color_manual(values = c("red", "blue")) +
    theme_minimal()
}

# Load datasets
liked <- read.csv("liked.csv")
other_liked <- read.csv("other_liked.csv")
conversation_quality <- read.csv("conversation_quality.csv")
video_conf_quality <- read.csv("video_conf_quality.csv")

# Run SRM GLMM for each dataset
run_srm_glmm(liked, "Liked (SRM Relationship)")
run_srm_glmm(other_liked, "Other Liked Me (SRM Relationship)")
run_srm_glmm(conversation_quality, "Conversation Quality (SRM Relationship)")
run_srm_glmm(video_conf_quality, "Video Conference Quality (SRM Relationship)")


```
